Monitoring forest health using hyperspectral imagery: Does feature selection improve the performance of machine-learning techniques?

### 2020-05-29 docs/00-manuscripts/ieee/ieee-manuscript.tex
mention the limitation of nrounds = 600

>>>>

The upper range of 600 used for hyperparameter {\texttt{nrounds}} for model XGBoost in this study could a potential limiting factor with respect to the performance of the datasets including NRI variables (\autoref{tab:hyperparameter_limits}).
This setting was a compromise between runtime and tuning space extension aimed to work well for most feature sets.
It could be that better predictive performances could have been achieved with a {\texttt{nrounds}} upper limit close to the number of features of the NRI datasets.
